Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-12 krs-survey.tex
Typos in the taxonomy nomenclature

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf E. Integration}
            child {node [taxon] {{\bf D.4} Performances}}
            child {node [taxon] {{\bf D.3} Monitoring}}
            child {node [taxon] {{\bf D.2} Executive layers}}
            child {node [taxon] {{\bf D.1} Sensori-motor}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf D.5 Performance \\Evaluation}
            child {node [taxon] {{\bf D.5.2} Cognitive Performances}}
            child {node [taxon] {{\bf D.5.1} Raw Performances}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}

>>>>

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf E. Integration}
            child {node [taxon] {{\bf E.4} Performances}}
            child {node [taxon] {{\bf E.3} Monitoring}}
            child {node [taxon] {{\bf E.2} Executive layers}}
            child {node [taxon] {{\bf E.1} Sensori-motor}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf E.4 Performance \\Evaluation}
            child {node [taxon] {{\bf E.4.2} Cognitive Performances}}
            child {node [taxon] {{\bf E.4.1} Raw Performances}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}
